---
title: "Retrieve Foursquare categories"
output: html_notebook
---

We need to retrieve the full list of foursquare categories to be used to label the different places found by our algorithm. Foursquare has an API that allows to do that. However, we will need a bit of coding to unpack the relevant info we need, which will come in json format.

#Load relevant packages and initialise credentials

```{r}
library("jsonlite")
library("dplyr")
library("stringr")
library("RCurl")

client_id <- "TRDTAHS4ZSJV2ROTNEQXVY5HE1DWOWJUJXIBSMQ1BUAD3DO1"

client_secret <- "ZCAEILOCQ4NGEOJIIJABRBAU3MPMWKLV3ABN5GACSSIBREY4"

```


#Interrogate Foursquare API

```{r}
categories_full <- getURL(str_c("https://api.foursquare.com/v2/venues/categories?",
                                "client_id=", client_id, "&",
                                "client_secret=", client_secret, "&",
                                "v=20180530", sep = "")) %>% 
                    fromJSON()
                     



```
#Explore response

```{r}
glimpse(categories_full$response$categories)

categories_full$response$categories
```


There are 10 "parent" categories in total, with each one that has more specific labels. We need to try to extract those labels. 

Let's have a look at the subcategories for the first main category. 


```{r}
glimpse(categories_full$response$categories$categories[1][[1]])

```

The information we need is *id, name, short name*. We need also to include *categories* because some categories have further subcategories too.

#Extract relevant info and create full category list

```{r}

tmp_cat <- categories_full$response$categories

categories_info <- NULL

for(i in 1:nrow(tmp_cat)){
  
  categories_info <- bind_rows(categories_info,
                               data.frame(
                               parent_id = tmp_cat$id[i],
                               tmp_cat$categories[[i]] %>% select(-icon)))
  
}

glimpse(categories_info)

```

The above works but this has to be iterated several times because of the different categories layers. With a while loop and updating the data frame in dynamically (e.g. adding rows to process in the tail) we should be able to do it.

```{r}

i <- 1

categories_info$processed <- FALSE # initialise control variable

while(sum(!categories_info$processed) > 0){ # until there are rows to process
  
  if(!is.null(unlist(categories_info$categories[i]))){ # if there are children nodes
    
    categories_info <- bind_rows(categories_info,
                                 data.frame(
                                 parent_id = categories_info$id[i],
                                 categories_info$categories[[i]] %>% select(-icon),
                                 processed = FALSE))
      
  }
  
  categories_info$processed[i] <- TRUE
  
  i <- i + 1
  
}

glimpse(categories_info)

```



